---
title: "Self Evaluation Exam 1 | Biologia Computacional 2022"
author: "Isabel Duarte"
date: "March 2022"
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Self Evaluation Exam

You have 60 minutes to complete the exercises. 
Good work.


### Load the dplyr package

The `dplyr` package will provide many useful data-manipulation functions, including a dataset (data frame) named `starwars` that we will use for this exercise.

```{r load_dplyr, exercise=TRUE}

# Load the required package:
library(dplyr)

# Print message
print ("Done")

```

### Create starwars dataframe

Save the `starwars` dataset to your own local variable; and remove all missing data, i.e. remove all NAs (Not Available - that means that there is no data available for that field).

```{r create_df, exercise=TRUE}

my_starwars <- na.omit(as.data.frame(starwars))

# Print message
print ("Done starwars")

```

## A. Getting to know the data

**Q1.** Inspect the `my_starwars` data frame.

```{r q1, exercise=TRUE, exercise.setup = "create_df", exercise.lines = 5}


```

```{r q1-hint}

# To look at the data, you can print it just by just typing its name.

```


**Q1.1.** To find documentation regarding the meaning of each variable, **read the help page** for the `starwars` (not the `my_starwars`) dataset.

```{r q1_1, exercise=TRUE, exercise.setup = "q1", exercise.lines = 5}



```

**Q2.** How many rows and how many columns are there in the `my_starwars` dataset?

```{r q2, exercise=TRUE, exercise.setup = "q1_1", exercise.lines = 5}



```

```{r q2-hint}

# You can look at the dimensions of your dataset with the function `dim()`

```

**Q3.** What are the column names of the `my_starwars` data frame?

```{r q3, exercise=TRUE, exercise.setup = "q2", exercise.lines = 5}



```

**Q4.** In general, rows in data frames refer to *observations*. Complete the following sentence (in english, no caps, without punctuation marks): 

```{r text_box, echo = FALSE}
question_text(
  "In the my_starwars dataset, each row refers to one ...",
  answer("Starwars character", message = "Don't forget to NOT capitalize."),
  answer("character from starwars", correct = TRUE),
  answer("personagem do starwars", message = "Correto, mas em Inglês."),
  answer("starwars character", correct = TRUE),
  allow_retry = TRUE
)
```


## B. Subset your data and dive into it

**Q5.** Create a new data frame named `starwars_small` containing all the rows and only the first 10 columns of **my_starwars**. We will now only work with the **starwars_small** data frame*.

```{r q5, exercise=TRUE, exercise.setup = "q3", exercise.lines = 5}



```

**Q6.** What is the data type of the first, second, and third columns of the `starwars_small` data frame.

```{r q6, exercise=TRUE, exercise.setup = "q5", exercise.lines = 5}



```

```{r q6-hint}

# You can use `str()` function to learn about data types of all your columns.

```

**Q7.** What is the mean, standard deviation, and median of the variable *height* from the `starwars_small` dataset?

```{r q7, exercise=TRUE, exercise.setup = "q6", exercise.lines = 10}



```

**Q7.1.** Can you look at the descriptive statistics of all variables in the `starwars_small` data frame?

```{r q7_1, exercise=TRUE, exercise.setup = "q7", exercise.lines = 10}



```

**Q8.** How many different hair colors exist in the `starwars_small` dataset?

```{r q8, exercise=TRUE, exercise.setup = "q7_1", exercise.lines = 10}



```

**Q9.** How many feminine characters have brown eye-color in the `starwars_small` data?   

```{r q9, exercise=TRUE, exercise.setup = "q8", exercise.lines = 10}



```

```{r q9-hint}

# Look at the `eye_color` and `gender` columns.

```

**Q10.** Which starwars characters are taller than Darth Vader (in the `starwars_small` data frame)?   

```{r q10, exercise=TRUE, exercise.setup = "q9", exercise.lines = 5}



```

```{r q10-hint}

# You can subset your dataset by asking for the rows for which the height is greater than Darth Vader's.

```


