---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ualg.compbio <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
<!-- badges: end -->

The goal of `{ualg.compbio}` is to provide the teaching materials for the
Computational Biology classes at UAlg, part of the curriculum of the Masters in
Biomedical Sciences.

## Installation

Make sure you have the `{remotes}` installed:

```r
install.packages('remotes')
```

Now you can install `{ualg.compbio}` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("instructr/ualg.compbio")
```

## Tutorials

To list the included tutorials in `{ualg.compbio}`:

```{r}
learnr::available_tutorials(package = 'ualg.compbio')
```

To run one of the tutorials included in `{ualg.compbio}` use the command
`learnr::run_tutorial()`. For example to run the interactive tutorial
`"self_eval_exam"`:

```r
learnr::run_tutorial('self_eval_exam', package = 'ualg.compbio')
```

To run the tutorial `"transcriptomics"`:

```r
learnr::run_tutorial('transcriptomics', package = 'ualg.compbio')
```
